\name{}: machine learning over interaction networks and ontology-based background knowledge predicts drug--target interactions

### 2021-07-01 paper/main.tex
.

Several of the biases we identify in evaluating DTI prediction methods
have been observed previously. The performance difference based on how
training and evaluation data is split (by interaction pair, by drug,
or by protein) has been demonstrated before using a
\todo{MacroAUC/MicroAUC???} measure \cite{}; we further extend on
these results by introducing performance measures based on micro
averages (Micro AUC$_p$ and Micro AUC_$d$) to further illustrate how
prediction performance changes when evaluation data is imbalanced. We
have further extended on prior results by introducing a ``na\"ive''
classifier that explicitly exploits one data bias to make predictions,
illustrating that this bias has a significant impact on DTI
methods. The bias we identify is similar to a previous bias found in
gene networks and methods that rely on the guilt-by-association
approach \cite{10.1371/journal.pcbi.1002444} but which has, to our
knowledge, not been demonstrated in the context of DTI prediction.

>>>>

Several of the biases we identify in evaluating DTI prediction methods
have been observed previously. The performance difference based on how
training and evaluation data is split (by interaction pair, by drug,
or by protein) has been demonstrated before using a
\todo{MacroAUC/MicroAUC???} measure \cite{}; we further extend on
these results by introducing performance measures based on micro
averages (Micro AUC$_p$ and Micro AUC_$d$) to further illustrate how
prediction performance changes when evaluation data is imbalanced. We
have further extended on prior results by introducing a ``na\"ive''
classifier that explicitly exploits one data bias to make predictions,
illustrating that this bias has a significant impact on DTI
methods. The bias we identify with the ``na\"ive'' classifier is
similar to a previous bias found in gene networks when using methods
that rely on the guilt-by-association principle
\cite{10.1371/journal.pcbi.1002444} but which has, to our knowledge,
not been demonstrated in the context of DTI prediction.
